Dominance Regions for Imaginary $\bfg$-vectors

### 2021-07-24 dominance_regions.tex
Committing to pull

@@

  \begin{align*}
    a
    &=-b_{41}b_{21}b_{32}b_{43}-b_{31}b_{21}b_{32}-b_{41}b_{21}b_{42}-b_{41}b_{31}b_{43}-b_{42}b_{32}b_{43}-b_{21}b_{21}-b_{31}b_{31}-b_{32}b_{32}-b_{41}b_{41}-b_{42}b_{42}-b_{43}b_{43}+4\\
    c
    &=-b_{21}b_{32}b_{43}b_{41}-b_{21}b_{32}b_{31}-b_{21}b_{42}b_{41}-b_{31}b_{43}b_{41}-b_{32}b_{43}b_{42}-b_{21}b_{21}-b_{31}b_{31}-b_{32}b_{32}-b_{41}b_{41}-b_{42}b_{42}-b_{43}b_{43}+4\\
    b
    &=b_{41} b_{32} b_{32} b_{41} - b_{31} b_{42} b_{32} b_{41} - b_{31} b_{43} b_{21} b_{42} - b_{41} b_{32} b_{31} b_{42} + b_{31} b_{42} b_{31} b_{42} + b_{21} b_{43} b_{21} b_{43} - b_{21} b_{42} b_{31} b_{43} - b_{21} b_{32} b_{31} - b_{31} b_{21} b_{32} - b_{21} b_{42} b_{41} - b_{31} b_{43} b_{41} - b_{32} b_{43} b_{42} - b_{41} b_{21} b_{42} - b_{41} b_{31} b_{43} - b_{42} b_{32} b_{43} - 2 b_{21} b_{21} - 2 b_{31} b_{31} - 2 b_{32} b_{32} - 2 b_{41} b_{41} - 2 b_{42} b_{42} - 2 b_{43} b_{43} + 6\\
    &=a+c-2+m\\
    &=a+c-2+n^2\\
    m
    &=b_{41}b_{21}b_{32}b_{43}+b_{21}b_{32}b_{43}b_{41}+b_{41}b_{32}b_{32}b_{41}-b_{31}b_{42}b_{32}b_{41}-b_{31}b_{43}b_{21}b_{42}-b_{41}b_{32}b_{31}b_{42}+b_{31}b_{42}b_{31}b_{42}+b_{21}b_{43}b_{21}b_{43}\\
    &\quad -b_{21}b_{42}b_{31}b_{43}\\
    &=(b_{31}b_{42}-b_{32}b_{41}-b_{21}b_{43})^2\\
    n
    &=b_{31}b_{42}-b_{32}b_{41}-b_{21}b_{43}\\
  \end{align*}

  Observe that $P(-1)=n^2$.
  What happens when $\lambda=\frac{-a+2\pm\sqrt{a(a-4)}}{2}$?  You get $P(\lambda)=(b-2)\lambda^2$.

>>>>

  \subsection{Deformation Support}
  The greedy basis of Lee, Li, and Zelevinsky \cite{???} can be defined as the positive pointed basis with minimal support.
  Here we identify the maximum possible support of its deformations.

  Consider the deformation of the theta basis element with $\bfg$-vector $\lambda$.
  \begin{theorem}
    For $\lambda\in\cI\cap\ZZ^2$, the support of any deformation of the corresponding theta basis element is contained in the polytope defined by the following inequalities:
    \begin{align*}
       \lambda_1-b\lambda_2 &\le x\\
       \lambda_2 &\le y\\
    \end{align*}
    is the convex hull of the following vertices:
    \[\lambda, \qquad (\lambda_1-b\lambda_2,\lambda_2), \qquad (\lambda_1-b\lambda_2,\lambda_2-c\lambda_1), \qquad (?,?)\]
    The $d$-vector is $(\lambda_1-b\lambda_2,\lambda_2)$

    $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2,c\lambda_1+2\lambda_2)$, and $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$

    Slope:
    \[\big(\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(c\lambda_1+2\lambda_2)-(\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)\big) /\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2)\]

    $y=$

    $(\lambda_1,\lambda_2)$ and $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$

    Slope: $-\frac{bc+\sqrt{bc(bc-4)}}{2b}$\\

    Corner of dominant support?: 
    \begin{align*}
      \left(\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2),-\frac{bc+\sqrt{bc(bc-4)}}{2b}\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2)+\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2\right)\\
      \left(\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2),-\frac{bc+\sqrt{bc(bc-4)}}{2b}\frac{bc}{\sqrt{bc(bc-4)}}\lambda_1+-\frac{bc+\sqrt{bc(bc-4)}}{2}\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\lambda_2+\lambda_2\right)\\
    \end{align*}

  \end{theorem}

@@

  \begin{align*}
    a
    &=-b_{41}b_{21}b_{32}b_{43}-b_{31}b_{21}b_{32}-b_{41}b_{21}b_{42}-b_{41}b_{31}b_{43}-b_{42}b_{32}b_{43}-b_{21}b_{21}-b_{31}b_{31}-b_{32}b_{32}-b_{41}b_{41}-b_{42}b_{42}-b_{43}b_{43}+4\\
    c
    &=-b_{21}b_{32}b_{43}b_{41}-b_{21}b_{32}b_{31}-b_{21}b_{42}b_{41}-b_{31}b_{43}b_{41}-b_{32}b_{43}b_{42}-b_{21}b_{21}-b_{31}b_{31}-b_{32}b_{32}-b_{41}b_{41}-b_{42}b_{42}-b_{43}b_{43}+4\\
    b
    &=b_{41} b_{32} b_{32} b_{41} - b_{31} b_{42} b_{32} b_{41} - b_{31} b_{43} b_{21} b_{42} - b_{41} b_{32} b_{31} b_{42} + b_{31} b_{42} b_{31} b_{42} + b_{21} b_{43} b_{21} b_{43} - b_{21} b_{42} b_{31} b_{43}\\
    &\quad - b_{21} b_{32} b_{31} - b_{31} b_{21} b_{32} - b_{21} b_{42} b_{41} - b_{31} b_{43} b_{41} - b_{32} b_{43} b_{42} - b_{41} b_{21} b_{42} - b_{41} b_{31} b_{43} - b_{42} b_{32} b_{43}\\
    &\quad - 2 b_{21} b_{21} - 2 b_{31} b_{31} - 2 b_{32} b_{32} - 2 b_{41} b_{41} - 2 b_{42} b_{42} - 2 b_{43} b_{43} + 6\\
    &=a+c-2+m\\
    &=a+c-2+n^2\\
    m
    &=b_{41}b_{21}b_{32}b_{43}+b_{21}b_{32}b_{43}b_{41}+b_{41}b_{32}b_{32}b_{41}-b_{31}b_{42}b_{32}b_{41}-b_{31}b_{43}b_{21}b_{42}-b_{41}b_{32}b_{31}b_{42}+b_{31}b_{42}b_{31}b_{42}+b_{21}b_{43}b_{21}b_{43}\\
    &\quad -b_{21}b_{42}b_{31}b_{43}\\
    &=(b_{31}b_{42}-b_{32}b_{41}-b_{21}b_{43})^2\\
    n
    &=b_{31}b_{42}-b_{32}b_{41}-b_{21}b_{43}\\
  \end{align*}

  Observe that $P(-1)=n^2$.
  What happens when $\lambda=\frac{-a\pm\sqrt{a^2-4}}{2}$?  You get $P(\lambda)=(b-2)\lambda^2$.
